---
title: "Cooking Recipes"
author: "Afton Coombs"
date: "5/21/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cooking Recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rdew)
```

## Introduction
`rdew` provides data about a number of aspects of the game, such as animals, crops, hats, quests, NPC's, locations, monsters, and more. This
is an example analysis using the cooking recipes dataset as well as the 
objects dataset, mean to demonstrate how to join a dataset to the objects
dataset to get info about objects that are dependencies.

## Cooking Recipes
The cooking recipes dataset contains information about recipes that can be cooked in your home kitchen. Some recipes require an unlock event, which can be found in the `unlock_conditions` columns. Recipes also require ingredients, which can be found in the `ingredients` column. Let's take a look.

```{r glimpse-of-cooking-recipes}
tibble::glimpse(cooking_recipes)
```

As we can see, `ingredients` has space-delimited integer values. Each of these space-delimited elements is the object id of an ingredient. How do we get more information about these items, such as the actual name of the item? By joining to the `objects` dataset!

## Joining to Objects
We will be joining to the object id's in the `objects` dataset.

```{r head-of-long-recipes}
head(cooking_recipes)
```

When we join the `cooking_recipes` dataset to the `objects` dataset, they should join on the columns `ingredient_id` and `object_id`, respectively. We'll use a left join because the objects dataset contains many ingredients.

There are some columns in here that aren't necessary, such as the 
`geode_possible_items`, since geodes aren't ingredients to cooking recipes. Those columns will have NA's for all rows.

```{r join-to-objects}
cooking_recipes_and_ingreds <-
  cooking_recipes %>%
  dplyr::left_join(objects, 
                   by = c("ingredient_id" = "object_id"),
                   suffix = c("_yield", "_ingredient"))

tibble::glimpse(cooking_recipes_and_ingreds)
```

Let's take a look at just the yield item and the required 
ingredients.

```{r head-just-items}
just_names <- 
  cooking_recipes_and_ingreds %>%
  dplyr::select(name_yield, 
                name_ingredient, 
                ingredient_id, 
                ingredient_quantity)

head(just_names)
```

