---
title: "Gift Tastes"
author: "Afton Coombs"
date: "8/29/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cooking Recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rdew)
```

## Introduction
`rdew` provides data about a number of aspects of the game, such as animals, crops, hats, quests, NPC's, locations, monsters, and more. This
is an example analysis using the NPC gift tastes dataset as well as the 
objects dataset, mean to demonstrate how to join a dataset to the objects
dataset to get info about what NPC's like or dislike. A related demonstration of joining a non-object dataset to an object dataset can be found in the Cooking Recipes vignette.

## NPC Gift Tastes
`npc_gift_tastes` contains data about gifts you can give to NPC's, and whether the NPC likes or dislikes that gift. This includes the `name` of the character, the `dialogue_type` (liked, loved, etc.), the `dialogue` the character will say upon receiving the gift, the `item_type` (liked, loved, etc.) and the `object_id`. Characters can like, love, hate, or feel neutral about an object. Let's take a look!

```{r glimpse-of-npc_gift_tastes}
tibble::glimpse(npc_gift_tastes)
```

There also exists a set of "universal gift tastes", which apply to all NPC's, and are found in `universal_gift_tastes`.

```{r glimpse-of-universal_gift_tastes}
tibble::glimpse(universal_gift_tastes)
```
Fortunately, there is a dataset `complete_npc_gift_tastes` which already combines these.

```{r glimpse-of-complete_npc_gift_tastes}
tibble::glimpse(complete_npc_gift_tastes)
```
