---
title: "Example Analysis: Hats & Achievements"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Analysis: Hats and Achievements}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rdew)
```

## Introduction
`rdew` provides data about a number of aspects of the game, such as animals, crops, hats, quests, NPC's, locations, monsters, and more. This
is an example analysis using the hats and achievements datasets, meant to demonstrate what you can do with this package.

## Hats
Hats data is available in the `hats` dataset. We can take a look at the variables and see it contains `object_id`, `description`, `skip_hair_draw`, `ignore_hairstyle_offset`, and `prismatic` (full documentation can be found with `?hats`).

```{r peek-at-hats}
head(hats)
```

## Achievements
Achievements exist in the `achievements` dataset, and contain the columns 
`id`, `name`, `description`, `display_on_collections_tab_before_earned`,
`prerequisite_achievement`, and `hat_earned`. 

Let's look at which hats are earned from which achievements. Hats are earned from certain in-game events, called achievements, so we can join achievements to hats
to get the full details of the hat earned for each achievement. We'll use
a left join here to only get the hats that are earned with an achievement, as 
there are even more hats that are just not earned with an achievement.

```{r join-achievements-and-hats}
achievements_and_hats <-
  rdew::achievements %>%
  dplyr::left_join(hats, 
                   by = c("hat_earned" = "object_id"), 
                   suffix = c("_achievement", "_hat"))

head(achievements_and_hats)
```

We get a few duplicate columns resolved with `_achievement` or `_hat`, but this is because
the column names overlapped, not because these should have been join columns (for
example, a description of a hat is different from a description of an achievement event).

```{r look-at-joined-data}
achievements_and_hats %>% 
  dplyr::select(name_achievement, 
                description_achievement, 
                name_hat, 
                description_hat)
```

If we take a look at the hat name and achievement name/description, we can see 
that some of them match the spirit of the event. For example, if you complete
the Fisherman achievement, you get a fisherman-style Sou'wester, and if you
complete the Cliques quest, you get a Tiara.

```{r look-at-aptly-named-data}
achievements_and_hats %>% 
  dplyr::filter(name_hat %in% c("Sou'wester", "Tiara")) %>%
  dplyr::select(name_achievement, 
                description_achievement, 
                name_hat, 
                description_hat)
```


